Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-03-28 demystify.tex
updates

\textbf{Advice}: You can explain about your school in your SOP (and also ask your LOR writer to do that). Of course, if you're interested in working with Vietnamese, consider  \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Viet-CS-Profs-US}{CS programs in the US that have Vietnamese professors}. %It might also be helpful to have your CS dept to put itself on CSRankings so that others know about the dept, its faculty, and research.

@@

\textbf{Advice}: As with school reputation, you can put a note about this in your statement and ask your LoR writers to talk about it.
Note that while having good grades at unknown school might not help,
having bad grades (e.g., < 3.0) will be \red{red flag} (unless your LORs or
statement give a proper explanation). This is especially true if you
have bad grades in relevant courses, e.g., Math and CS.

>>>>

\textbf{Advice}: If you think your school is the top in your country but might not be well-known internationally, you should talk about it in your SOP (and also ask your LOR writer to do that). Of course, if you're interested in working with Vietnamese, consider  \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Viet-CS-Profs-US}{CS programs in the US that have Vietnamese professors}. %It might also be helpful to have your CS dept to put itself on CSRankings so that others know about the dept, its faculty, and research.

@@

\textbf{Advice}: As with school reputation, you can put a note about this in your statement and ask your LoR writers to talk about it.
Note that while having good grades might not help much,
having bad grades (e.g., < 3.0) will be \red{red flag} (unless your LORs or
statement give a proper explanation). This is especially true if you
have bad grades in relevant courses, e.g., Math and CS.
